\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip}
\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}
\usepackage{tabularx}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[style=authoryear,sorting=ynt,maxbibnames=2]{biblatex}
\usepackage[unicode,draft=false]{hyperref}
\usepackage{fontawesome5}

\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{5pt}

\begin{document}

\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Harshvardhan Patil} \\[5pt]
\href{https://github.com/harshvardhanpatil}{\raisebox{-0.05\height}\faGithub\ harshvardhanpatil} \ $|$ \ 
\href{https://www.linkedin.com/in/harshvardhan-patil-23b7b9180/}{\raisebox{-0.05\height}\faLinkedin\ Linkedin} \ $|$ \ 
\href{mailto:harshpatil1606@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ harshpatil1606@gmail.com} \ $|$ \ 
\href{tel:+44 7776532469}{\raisebox{-0.05\height}\faMobile \ +44 7776532469} \\
% add location
Liverpool, United Kingdom \\
\end{tabularx}

\section{About}
Dedicated Software Developer with 3 years of experience specializing in full-stack development and cloud-based solutions. Proven track record of delivering high-performance applications at PwC, with a focus on scalability and data visualization. Currently pursuing an MSc in Advanced Computer Science, seeking opportunities in cloud computing, software engineering, and machine learning to drive innovation and efficiency in leading organizations.

\section{Experience}
\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Senior Associate} \textit{- PwC, India (Product and Innovation Team)} & \hfill Sept 2020 - Aug 2023 \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item Optimized data visualization for over 50 million records by developing high-performance web dashboards using ReactJS, D3.js, and Apex Charts, improving decision-making speed for internal teams by 25\%.
    \item Enhanced system efficiency by leading the implementation of Azure Function Apps with orchestrator functions, reducing application response time by 20\% and supporting seamless integration of machine learning models across various products.
    \item Spearheaded the design and development of scalable full-stack solutions with Node.js and React, ensuring robust application performance and improving service uptime critical business applications.
    \item Led cross-platform integration initiatives, developing reusable D3.js components that increased productivity and reduced development time by 300+ recorded hours saved.
    \item Optimized data pipelines using Python, automating data cleaning processes and reducing manual intervention, which enhanced data usability for business intelligence applications.
    \item Pioneered the deployment of Microsoft Power Apps and Power Pages, introducing low-code/no-code solutions that reduced development time for client-facing applications by up to 35\%.
\end{itemize}
}  \\
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Intern} \textit{- Padmajeet Infotech, India (Android and Java Developer)} & \hfill Jul 2019 - Oct 2019 \\
\multicolumn{2}{@{}X@{}}{
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item Developed and enhanced key features for an Android-based e-commerce application, improving user interface efficiency and increasing customer engagement by 15\%.
    \item Optimized back-end infrastructure, improving query execution time by integrating efficient ORM techniques, handling over 500 database transactions per day with reduced latency.
    \item Worked closely with a team of five developers in an Agile environment, contributing to sprint planning and feature delivery, ensuring on-time completion of critical project milestones.
    \item Ensured code quality and system scalability by adhering to enterprise-level standards and conducting thorough testing.
\end{itemize}
}
\end{tabularx}

\section{Skills}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{Technical Skills:} ReactJS, NodeJS, Python, Docker, Kubernetes, Fast API, .NET, Django, ORM, Java, Spring Framework, RESTful APIs, Websockets, Rabbit MQ, Azure Function Apps, Microsoft Power Apps, Power Pages, JavaScript, TypeScript, HTML, CSS, Bootstrap, Tailwind CSS, React Native.
    \item \textbf{Data Engineering:} Apache Spark, Hadoop
    \item \textbf{Cloud:} Azure Cloud Services, AWS
    \item \textbf{Visualization:} D3JS, Apex Charts, High Charts, Tableau
    \item \textbf{Databases:} MySQL, Oracle, PostgreSQL, MongoDB
    \item \textbf{Tools:} Git, Visual Studio, VS code, GitHub, Postman
    \item \textbf{Others:} Problem-solving, Attention to detail, Communication and teamwork
\end{itemize}

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}} 
2023 - present & MSc Advanced Computer Science at \textbf{Newcastle University} \hfill \normalsize  \\
2016 - 2020 & B.E. in Computer Science at \textbf{Visvesvaraya Technological University} \hfill (CGPA: 7.17) \\
2014 - 2016 & Class 12th Science with Computer Science Major at \textbf{Alvas College} \hfill  (84 Perc.) \\
\end{tabularx}

\section{Recent Projects}
\begin{itemize}[leftmargin=*]
    \item \textbf{Secure Chat Application} \\
    \textit{Academic Group Project} \\
    This chat application had functionalities like E2E encryption, Secure File Transfer, OAuth 2.0, instant message sharing, etc. security was taken as the top most priority in development of this application. Various technologies like FastAPI, websockets, React, Redis, PostgreSQL where used.
    \item \textbf{Premier League Prediction Application} \\
    \textit{DurHack Hackathon Project} \\
    Developed a software application for predicting Premier League football match outcomes using predictive analytics and machine learning. Project uses technologies like FastAPI, Rabbit MQ, ReactJS, Machine Learning, Prostgre SQL, etc.
    \item \textbf{Driver Vigilance System} \\
    \textit{Deep Learning and Computer Vision Project} \\
    Developed a system to enhance road safety by detecting risky driver behaviors using deep learning and computer vision. Responsibilities included implementing and fine-tuning convolutional neural networks, preprocessing data, designing a user interface, and evaluating model performance. Technologies used: Python, TensorFlow, OpenCV, Scikit-learn
\end{itemize}


\section{Key Achievements}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{Winner - Smart India Hackathon} \textit{(Aug 2020) Team Leader} \\
    \textit{Ministry of Health and Family Welfare (Govt. of India)} \\
    Led Team ABHYUDAY to victory in Smart India Hackathon, one of India's largest hackathons, endorsed by the Ministry of Health and Family Welfare. Developed an Android application designed to improve response times and services in medical emergencies, addressing problem statement SS-42. Engineered and deployed the application over a challenging 3-day period, focusing on reliable functionality under high-stress, emergency conditions.
    \item \textbf{4th Place - Eyantra Robotics Competition} \textit{(Mar 2019) Team Member} \\
    \textit{Indian Institute of Technology, Bombay} \\
    Secured 4th place in the nationwide Eyantra Robotics hackathon hosted by IIT Bombay. Collaborated in a team to design and build a robot for the Nutty Squirrel challenge over a six-month period. Engineered a solution that demonstrated innovative robotics applications in simulated real-world problem-solving.
\end{itemize}

\section{Certifications}
\begin{itemize}[noitemsep,topsep=0pt,parsep=0pt,itemsep=-3pt,leftmargin=*]
    \item \textbf{Microsoft Certified: Azure Fundamentals} \hfill Issued Apr 2023 \\
    \item \textbf{PwC Certified: Digital Acumen} \hfill Issued Oct 2020 \\
    \item \textbf{PwC Certified: Human-Centered Design} \hfill Issued Oct 2020 \\
    \item \textbf{HackerRank Certified - Python (Basic) Certificate} \hfill Issued Sep 2020 \\
\end{itemize}

% White scripting


\vfill
\center{\footnotesize Last updated: \today}
\end{document}
